Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Update figshare access dates

\bibitem[Bachant and Wosnik(2014)]{Bachant2014-RVAT-CAD}
Bachant, P.; Wosnik, M.
\newblock {UNH-RVAT CAD Models}.
\newblock \hl {Fig\textbf{share}}. 
%Is it necessary to make the type of share bold?
Available online: 
 \url{http://dx.doi.org/10.6084/m9.figshare.1062009} (accessed on \hl{Day Month} 2014).

\bibitem[Bachant and Wosnik(2015)]{Bachant2015-RVAT-Re-dep-data}
Bachant, P.; Wosnik, M.
\newblock {UNH-RVAT} {R}eynolds Number Dependence Experiment: Reduced Dataset
 and Processing Code.
\newblock Fig\textbf{share}. Available online: 
 \url{http://dx.doi.org/10.6084/m9.figshare.1286960} (accessed on \hl{Day Month} 2015).

\bibitem[Coleman and Steele(2009)]{ColemanSteele}
Coleman, H.W.; Steele, W.G.
\newblock {\em Experimentation, Validation, and Uncertainty Analysis for
 Engineers}, 3rd ed.; John~ Wiley \& Sons: \hl{ Hoboken, NJ, USA,} 2009.

\bibitem[Drela(1989)]{Drela1989}
Drela, M.
\newblock XFOIL: An Analysis and Design System for Low Reynolds Number
 Airfoils. In {\em Low Reynolds Number Aerodynamics}; Lecture Notes in Engineering; Springer Verlag: \hl{Berlin, Germany,} 1989;
 Volume~54.

>>>>

\bibitem[Bachant and Wosnik(2014)]{Bachant2014-RVAT-CAD} Bachant, P.; Wosnik, M.
\newblock {UNH-RVAT CAD Models}. \newblock Fig\textbf{share}. Available online:
\url{http://dx.doi.org/10.6084/m9.figshare.1062009} (accessed on 20 June 2014).

\bibitem[Bachant and Wosnik(2016)]{Bachant2015-RVAT-Re-dep-data} Bachant, P.;
Wosnik, M. \newblock {UNH-RVAT} {R}eynolds Number Dependence Experiment: Reduced
Dataset and Processing Code. \newblock Fig\textbf{share}. Available online:
\url{http://dx.doi.org/10.6084/m9.figshare.1286960} (accessed on 22 January
2015).

\bibitem[Coleman and Steele(2009)]{ColemanSteele} Coleman, H.W.; Steele, W.G.
\newblock {\em Experimentation, Validation, and Uncertainty Analysis for
    Engineers}, 3rd ed.; John~ Wiley \& Sons: Hoboken, NJ, USA, 2009.

\bibitem[Drela(1989)]{Drela1989} Drela, M. \newblock XFOIL: An Analysis and
Design System for Low Reynolds Number Airfoils. In {\em Low Reynolds Number
    Aerodynamics}; Lecture Notes in Engineering; Springer Verlag: Berlin, Germany,
1989; Volume~54.
